Testable normative theories

### 2020-05-20 simple.tex
Renamed Negation coherence by Interpretability.
This is not only about negation coherence (phi in implies ¬\phi out), but also about restricted completeness (one of phi in or ¬\phi in).

\begin{proposition}[Internal negation coherence]
	\label{th:intnegcoh}
	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \Box\Phi \oplus ¬\phi \in \Box\Phi$.
\end{proposition}
\begin{proof}
	Consider $\phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]$. Proving \cref{th:intnegcoh} only requires to show that $\phi \in \Box\Phi ⇒ ¬\phi \notin \Box\Phi$. By definition, $\phi \in \Box\Phi$ implies that $\exists \ar \suchthat \ar \ileadstost[pos] \phi$, and the implication is thus proven by using \cref{prop:protcoh}: $\phi \in \Box\Phi ⇒ [\exists \ar \suchthat \ar \ileadstost[pos] \phi] ⇒ ¬[\exists \ar \suchthat \ar \ileadstost[pos] ¬\phi] ⇒ \phi \notin \Box\Phi$.
\end{proof}
\begin{definition}[Restricted negation coherence]
	\label{def:restrnegcoh}
	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \iPhi \oplus ¬\phi \in \iPhi$.
\end{definition}
\begin{proposition}[Restricted negation coherence satisfaction]
	Under \cref{ax:nocontr,ax:norm}, all models satisfy Restricted negation coherence.
\end{proposition}
\begin{proof}
	This follows from \cref{th:intnegcoh}.
\end{proof}

>>>>

\begin{proposition}[Internal interpretability]
	\label{th:intinterpr}
	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \Box\Phi \oplus ¬\phi \in \Box\Phi$.
\end{proposition}
\begin{proof}
	Consider $\phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]$. Proving the claim only requires to show that $\phi \in \Box\Phi ⇒ ¬\phi \notin \Box\Phi$. By definition, $\phi \in \Box\Phi$ implies that $\exists \ar \suchthat \ar \ileadstost[pos] \phi$, and the implication is thus proven by using \cref{prop:protcoh}: $\phi \in \Box\Phi ⇒ [\exists \ar \suchthat \ar \ileadstost[pos] \phi] ⇒ ¬[\exists \ar \suchthat \ar \ileadstost[pos] ¬\phi] ⇒ \phi \notin \Box\Phi$.
\end{proof}
\begin{definition}[Restricted interpretability]
	\label{def:restrinterpr}
	$\forall \phi \suchthat [\phi \in \Box\Phi \lor ¬\phi \in \Box\Phi]: \phi \in \iPhi \oplus ¬\phi \in \iPhi$.
\end{definition}
\begin{proposition}[Restricted interpretability satisfaction]
	All models satisfying \cref{ax:nocontr,ax:norm} also satisfy Restricted interpretability.
\end{proposition}
\begin{proof}
	This follows from \cref{th:intinterpr}.
\end{proof}
